\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-11 fully-abstract-comp/popl2019/paper.tex
Added new first line to introduction.

\section{Introduction}
\label{sec:introduction}
\todo[inline]{Add a sentence or two about secure compilation to ease the start.}
Secure compilers preserve source-language (security-relevant) properties even when the compiled code interacts with arbitrary target-language components.
Generally, properties that hold in the source language but not in the target language need to be somehow enforced by the compiler.
Two properties that hold in many high-level source languages, but not in the assembly languages they are compiled to, are well-bracketed control flow and encapsulation of local state.

>>>>

\section{Introduction}
\label{sec:introduction}
Secure compilation is an active topic of research (e.g.~\citep{devriese_modular_2017,patrignani_hyper_2017,abate_good_components_2018,new_universal_embedding_2016,juglaret_beyond_2016}), but a real secure compiler is yet to be made.
Secure compilers preserve source-language (security-relevant) properties even when the compiled code interacts with arbitrary target-language components.
Generally, properties that hold in the source language but not in the target language need to be somehow enforced by the compiler.
Two properties that hold in many high-level source languages, but not in the assembly languages they are compiled to, are well-bracketed control flow and encapsulation of local state.
